Proposed Solution

### 2017-01-22 CAV17/secs/arch.tex
reword to academic stlye

\para{Rule refinement.}
\ennan{It seems so far I do not know how exactly this part works. 
Maybe we can write through this part after finish the 
section 6.}

>>>>

\para{Post Analysis.}
Finally, the logically structured representation of learned rules allows for a further post analysis stage.
This novel extension infers knowledge on the accepted rules that can improve the output of the system..
As a case study, we build a graph to model the learned rules.
We analyze the properties of this graph to construct an ordering of rules by their importance, 
  as well as to produce a measure of complexity for any configuration of the target system.
While the metrics in used in \app are effective, they are not intended to be exhaustive.
The information contained in the structured representation of the learned rules, 
  is a unique benefit of the learning algorithm, as contrasted with other machine learning techniques.
